\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
do not rush kostas

\medskip
Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ ins introduced into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2}) 
as the presence of this extra inlet increases the flow at the top layers. At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when VR=$100$, 
%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
it is a test-case that can illustrate the higher, faster and more profound development of instabilities. Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio. A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$. No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes). The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$. Screenshots of the phase volume fraction and the development of fingers are shown in figures \ref{fig:4testcase_a}-\ref{fig:4testcase_b}.

>>>>

\medskip
Figure \ref{fig:3testcase_a} illustrates another set of simulations for when another region (inlet) of fluid $1$ has introduced into the formation. This time fluid $1$ is injected from both the left hand side and the upper left corner of the domain, at a velocity u=$0.5$ while the set up of the problem remains the same, the mobility ratio is $10$, and the adaptive and ustructured mesh is implied. The top layer is saturated with phase $2$, while the rest of the domain has a saturation of $0.1$. The major difference is located in the velocity fields %(see Fig.\ref{fig:vel_magn2}) 
as the presence of this extra inlet increases the flow at the top layers. At this point is proper to mentioned the extreme case, see Fig.\ref{fig:4testcase}, when mobility ratio is even an order of magnitude higher, when VR=$100$, 
%this case is unlikely to happen as the mobility ration of the existing fluids in the industry , 
it is a test-case that can illustrate the higher, faster and more profound development of instabilities. Also by focusing the grid resolution in the saturation front, \citet{christou_2015}  demonstrated the explicit formation of fingers formed due to the instability in the pressure ﬁeld and triggered by viscosity ratio. A comparison has also been made by using a low resolution element, the $P_{1}DG-P_{1}DG$. No fingers could be observed due to mesh coarseness (fingers were observed in ﬁner uniform and adaptive meshes). The last case that will give an estimable and quantitative description to the reader is the when the mobility ration is highly increased into $100$. Screenshots of the phase volume fraction and the development of fingers are shown in figures \ref{fig:4testcase_a}-\ref{fig:4testcase_b}.
